Pre-processing high frequency animal tracking data

### 2020-08-25 02_filtering_data.Rmd
add to simulation function

```{r function_add_outliers}
# function for point outliers
do_add_outliers <- function(data, p_data = 0.1, std_dev = 0.05) {
  n_rows <- floor(p_data * nrow(data))
  tmp_data <- copy(data)

  tmp_data[sample(nrow(data), n_rows),
            c("x", "y") := lapply(.SD,
                                  function(z) {
                                    z + stats::rnorm(n_rows, sd = std_dev)
                                  }),
            .SDcols = c("x", "y")]
  return(tmp_data)
}
```

@@

```{r}
sim_data <- mapply(function(p_outlier, ext_outlier) {
  # make simulated data
  this_data <- do_smoove_data()

  # extract 'true' movement metrics
  speed <- atl_get_speed(this_data, type = "in")

  # extract proportion of landscape used
  land_vals <- extract(landscape,
                       this_data[, c("x", "y")])

  land_vals <- as.data.table(table(landscape))

  # what to return

  # WORK IN PROGRESS HERE

  error_data <- do_add_outliers(this_data, 
                                p_data = p_outlier,
                                std_dev = ext_outlier)
  return(error_data)
}, 
param_c$p_outlier, 
param_c$ext_outlier, 
SIMPLIFY = FALSE)
```

>>>>

```{r function_add_outliers}
# function for point outliers
do_add_outliers <- function(data, p_data = 0.1, std_dev = 0.05) {
  n_rows <- floor(p_data * nrow(data))
  tmp_data <- data.table::copy(data)

  tmp_data[sample(nrow(data), n_rows),
            c("x", "y") := lapply(.SD,
                                  function(z) {
                                    z + stats::rnorm(n_rows, sd = std_dev)
                                  }),
            .SDcols = c("x", "y")]
  return(tmp_data)
}

# functions for extracting and tallying landscape values
do_count_landcover <- function(land, track) {
  land_values <- raster::extract(land, track[, c("x", "y")])
  land_values <- data.table::as.data.table(table(land_values))
  land_values[, p_land := N / sum(N)]
  return(land_values)
}
```

@@

```{r}
sim_data <- mapply(function(p_outlier, ext_outlier) {
  # make simulated data
  ref_data <- do_smoove_data()

  # extract 'true' movement metrics
  speed <- atl_get_speed(ref_data, type = "in")
  land_vals <- do_count_landcover(landscape, ref_data)
  lands_vals[, type := "reference"]

  # now add error
  error_data <- do_add_outliers(this_data, 
                                p_data = p_outlier,
                                std_dev = ext_outlier)

  # get movement metrics with error
  error_speed <- atl_get_speed(error_data, type = "in")
  error_land_vals <- do_count_landcover(landscape, error_data)
  error_land_vals[, type := "outliers"]

  # now clean data
  clean_data <- copy(error_data)
  clean_data[, `:=`(in_speed = atl_get_speed(clean_data, type = "in"),
                    out_speed = atl_get_speed(clean_data, type = "out"),
                    angle = atl_turning_angle(clean_data))]
  upper_speed_cutoff <- stats::quantile(clean_data$in_speed, probs = 0.9)
  angle_cutoff <- 40
  clean_data <- atl_filter_covariates(clean_data,
                                      filters = c(glue('{c("in_speed", 
                                                           "out_speed")} < 
                                                         {upper_speed_cutoff}'),
                                                  glue('angle < {angle_cutoff}')
                                                  )
                                      )

  # get speed and land proportion
  clean_speed <- atl_get_speed(clean_data, type = "in")
  clean_land_vals <- do_count_landcover(landscape, clean_data)
  clean_land_vals[, type := "cleaned"]

  # synthesize data
  land_props <- rbindlist(land_vals, error_land_vals, clean_land_vals)
  setnames(land_props, old = "V1", new = "landcover")
  # count proportion
  land_props <- dcast(land_props, landcover ~ type, value.var = "p_land")

  return(errorCondition("WORK IN PROGRESS"))
}, 
param_c$p_outlier, 
param_c$ext_outlier, 
SIMPLIFY = FALSE)
```
